Requiem for a Balanced Life: Analysis of My Behavioural Patterns as a PhD Student

### 2023-04-03 outputs/paper/timesheet_analysis.qmd
minor updates
Fix typo in GitHub link

---
title: "Requiem for a Balanced Life: Analysis of My Behavioural Patterns as a PhD Student"
title-block-banner: true
abstract: "Various studies have shown that PhD students are having trouble with their work-life balance and coping with the stress of their workloads. To understand my own time management skills, I analyzed my timesheet data to understand my behavioural patterns over the first two semesters of my PhD journey. I found that I am spending about 40 hours a week, with most of my time spent on research, course work, and teach assistant related activities. There is evidence of improper work-life balance based on my tendency to work in late evenings as well as on weekends. To strive for better balance, I have outlined several suggestions to purposefully plan for each day, as well as created prediction models to estimate and plan for upcoming projects."
thanks: "Code and data supporting this analysis is available at: hhttps://github.com/christina-wei/PhD-Time-Analysis.git"
author: Christina Wei
date: today
date-format: long
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: ref.bib
---

@@

\<Data not complete - before and after\>

-   Sleep data - automatically tracked through Fitbit

-   Deliverable data - created at the beginning of each term to track major deliverables

-   Missing - social aspects, quality of work

-   Time fixed by events - like going to school, meetings that I do not control

@@

\newpage
# Appendix {.unnumbered}

@@

\newpage
# Reference

>>>>

---
title: "Requiem for a Balanced Life: Analysis of My Behavioural Patterns as a PhD Student"
title-block-banner: true
abstract: "Various studies have shown that PhD students are having trouble with their work-life balance and coping with the stress of their workloads. To understand my own time management skills, I analyzed my timesheet data to understand my behavioural patterns over the first two semesters of my PhD journey. I found that I am spending about 40 hours a week, with most of my time spent on research, course work, and teach assistant related activities. There is evidence of improper work-life balance based on my tendency to work in late evenings as well as on weekends. To strive for better balance, I have outlined several suggestions to purposefully plan for each day, as well as created prediction models to estimate and plan for upcoming projects."
thanks: "Code and data supporting this analysis is available at: https://github.com/christina-wei/PhD-Time-Analysis.git"
author: Christina Wei
date: today
date-format: long
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: ref.bib
---

@@

@@

\newpage

# Appendix {.unnumbered}

@@

\newpage

# Reference
